Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE)

### 2014-02-05 WSSSPE1_report/WSSSPE1_summary_report.tex
Section 3 Keynote: turn presentations and URLs into references
Section 3 Keynote: turn a URL into a reference

The first
keynote~\cite{WSSSPE1-keynote1}
was delivered by Philip E. Bourne of University of California, San Diego.  Bourne is a basic biomedical scientist but has formed four software
companies. He also helped found PLOS and
PDB\footnote{\url{http://www.rcsb.org/pdb/home/home.do}}.  He is
working on automating three-dimensional visualizations of cell
contents and molecular structures, a problem that has not been solved
and would serve as a key function of software in biomedical sciences.

@@

The second keynote~\cite{WSSSPE1-keynote2}\footnote{\url{}} was by
 Arfon Smith\footnote{\url{http://arfon.org/}} of Github.

>>>>

The first
keynote~\cite{WSSSPE1-keynote1}
was delivered by Philip E. Bourne of University of California, San Diego.  Bourne is a basic biomedical scientist but has formed four software
companies. He also helped found PLOS and
PDB~\cite{PDB}.  He is
working on automating three-dimensional visualizations of cell
contents and molecular structures, a problem that has not been solved
and would serve as a key function of software in biomedical sciences.

@@

The second keynote~\cite{WSSSPE1-keynote2} was delivered by
 Arfon Smith of GitHub.
